### 2021-04-05 Chapter-4/Chapter-4.tex
update

\subsection{Model Leakages}
\section{Approximate Model Counting}
\label{MCreasons}
According to
Definition~\ref{chapter4:def} introduced in the previous section,
the problem of quantifying the amount of leaked information can be reduced to
the problem of computing the number of items in $K^o$. However, we find that while
there are various propositional model counters (e.g., \#SAT), they are not
sufficient scalable for production cryptosystem analysis.
there is no open source modulo theories counter (\#SMT) available.

@@

\begin{theorem}
    \label{IndependentConstraint}
    Let $g_{1}, g_{2}, \ldots, g_{m}$ be a maximum independent partition of
    $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
    $K_c$ is the input set that satisfies constraint $c$. We have the following
    equation in regard to the size of $K_c$
    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}|*|K_{g_{2}}|*\ldots*|K_{g_{n}}|$$
\end{theorem}
\vspace{-3pt}
With Theorem~\ref{IndependentConstraint}, we change the problem of
counting the number of solutions to a complicated constraint in a high-dimension
space into counting solutions to several small constraints. We compute the
maximum independent partition by iterating each $\addr{i}$ and applying the function
$\pi$ over the constraint $\addr{i}$.

@@

%% \IncMargin{1em}
%% \begin{algorithm}[h]
%%       \DontPrintSemicolon
%%       \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
%%       \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
%%       \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
%%       \For{$i\leftarrow 1$ \KwTo $n$}
%%       {
%%             $S_{c_i}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
%%             \For{$g_{i} \in G$}
%%             {
%%                   $S_{g_i}$ $\leftarrow$ $\pi(g_{i})$ \;
%%                   $S$ $\leftarrow$ $S_{C_i} \cap S_{G_i}$  \;
%%                   \If{$S \neq \emptyset$}
%%                   {
%%                         $g_{i} \leftarrow g_{i} \land g_{\addr{i}}$ \;
%%                         \textbf{break} \;
%%                   }
%%                   Insert $c_{\addr{i}}$ to $G$
%%             }
%%       }
%%       \caption{The Maximum Independent Partition}
%%       \label{algo:max-inde}
%% \end{algorithm}
%% \DecMargin{1em}

@@

    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * range(k))$
    \caption{Multiple Step Monte Carlo Sampling}
\end{algorithm}
\DecMargin{1em}
%% the algorithm
%\IncMargin{1em}
%\begin{algorithm}
%\SetAlgoLined
%\DontPrintSemicolon

%\KwIn{{The constraint $G_{i}= C_{i_1} \land C_{i_2}
%\land \ldots \land C_{i_m}$}}    
%\KwOut{{The number of assignments that satisfy $G_{i}$ $|K_{G_{i}}|$}}

%\SetKwProg{RW}{RandomWalk}{}{}
%\SetKwProg{MM}{MetropolisMove}{}{} 
%$n$: the number of sampling times \;
%$P$: a probability generator \;
%$k$: the input assignment \;
%$n_{s}$: the number of satisfying assignments \;
%$\#k$: the satisfying number of k \fixme{this number is not used syntactically} \; 
%Initialization: \;
%$\#{k_0}$ $\leftarrow$ $\sum_{j=1}^{m}C_{i_j}(k_0)$ \;
%\For{$t\leftarrow 1$ \KwTo $n$} {
%      $p$ $\leftarrow$ $P$ \;
%      \If{$p \geq 0.5$}
%      {
%        $v$ $\leftarrow$ \RW{$v$} {}
%      }
%      \Else{
%            $v$ $\leftarrow$ \MM{$v$} {}
%      }
%      \If{$v$ satisfies $G_{i}$}
%      {$n_{s}$ $\leftarrow$ $n_{s} + 1$}
%}
%$|K_{G_{i}}|$ $\leftarrow$ $n_s|K| / n$
%\caption{Metropolis Sampling}
%\end{algorithm}
%\DecMargin{1em}

@@

%    \resizebox{1.9\columnwidth}{!}{
    \begin{threeparttable}
    \begin{tabular}{l@{}r@{~~}rrr@{~~}rr}
        \hline
        \textbf{Name}   & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
                           & \textbf{\# Instructions}    & \textbf{SE} & \textbf{MC}                                                    \\\hline
                                                 &                        &                     &                      &              & ms        & ms              \\\cline{6-7}
        AES\tnote{1}               & 68                     & 0                   & 68                   & 39,855        & 512     & 1,052         \\
        AES\tnote{2}                & 68                     & 0                   & 68                   & 39,855       & 520    & 1,057         \\
        AES\tnote{4}                & 75                     & 0                   & 75                   & 1,704        & 231    & 9,199        \\
        AES\tnote{5}                & 88                     & 0                   & 88                   & 1,350        & 36      & 1,924         \\
        AES\tnote{6}                & 88                     & 0                   & 88                   & 1,350        & 35      & 1,961        \\
        AES\tnote{7}                & 88                     & 0                   & 88                   & 1,420        & 36     & 2,161        \\
        AES\tnote{8}                & 88                     & 0                   & 88                   & 1,586        & 43      & 1,631        \\
        DES\tnote{1}                & 15                     & 0                   & 15                   & 4,596        & 58      & 162          \\
        DES\tnote{2}                & 15                     & 0                   & 15                   & 4,596        & 57      & 162           \\
        DES\tnote{4}                & 6                      & 0                   & 6                    & 2,976         & 163    & 4,677         \\
        DES\tnote{5}                & 8                      & 0                   & 8                    & 2,593         & 166    & 6,509        \\
        DES\tnote{6}                & 8                      & 0                   & 8                    & 2,593        & 165    & 5,975        \\
        DES\tnote{7}                & 8                      & 0                   & 8                    & 4,260         & 182    & 5,292        \\
        DES\tnote{8}                & 6                      & 0                   & 6                    & 8,272         & 229     & 5,152      \\
                           &                        &                     &                      &                  & seconds   & seconds               \\\cline{6-7}
        Chacha20\tnote{3}           & 0                      & 0                   & 0                    & 149,353        & 2     & 0             \\  
        Poly1305\tnote{3}           & 0                      & 0                   & 0                    & 1,213,937      & 15    & 0             \\
        Argon2i\tnote{3}            & 0                      & 0                   & 0                    & 4,595,142       & 37    & 0             \\
        Ed25519\tnote{3}            & 0                      & 0                   & 0                    & 5,713,619       & 271   & 0            \\
        ECDSA\tnote{1}              & 6                      &    6                & 0                    &  4,214,946     &  48   &   31       \\ 
        ECDSA\tnote{2}              &   4                   &   4                 & 0                    &  4,192,558    & 102   & 1639          \\   
        ECDSA\tnote{5}              &  5                    & 4                   & 1                    &  8,248,322       & 101     & 62           \\   
        ECDSA\tnote{6}              &  5                    & 4                   & 1                    &  8,263,599      & 100     & 58            \\   
        ECDSA\tnote{7}              &  5                    & 4                   & 1                    &  6,100,465       & 76      & 42                  \\  
        ECDSA\tnote{8}              & 0                      &  0                   &    0               &  10,244,076       &  121     & 0                  \\  
        ECDSA\tnote{9}              & 0                      &  0                   &  0                 &  9,266,191          & 102     & 59        \\

                           &                        &                     &                      &                 & minutes   & minutes         \\\cline{6-7}
        RSA\tnote{1}                & 6                       & 6                   & 0                    & 22,109,246    & 39     & 41           \\
        RSA\tnote{2}                & 12                      & 12                  & 0                    & 24,484,441    & 44     & 251           \\
        RSA\tnote{4}                & 107                    & 105                 & 2                    & 17,002,523   & 23      & 428           \\
        RSA\tnote{5}                & 38                     & 27                  & 11                   & 14,468,307   & 29     & 436          \\
        RSA\tnote{6}                & 36                     & 27                  & 9                    & 15,285,210   & 40     & 714          \\
        RSA\tnote{7}                & 31                     & 22                  & 9                    & 16,390,750   & 34      & 490         \\
        RSA\tnote{8}                & 4                      &  4                  & 0                    & 18,207,016   & 8      & 53          \\
        RSA\tnote{9}                & 8                      &  8                  & 0                    & 18,536,796    & 5      & 780         \\
        RSA\tnote{10} & 11& 9& 2& 9,527,231& 2 &38\\
        RSA\tnote{11} & 14& 14& 0& 10,513,606& 14 &503 \\
        RSA\tnote{12}               & 8                      &  8                  & 0                    & 27,407,986    & 113    & 6560       \\

>>>>

\subsection{Model Leakages}
\section{Approximate Model Counting}
\label{MCreasons}
In the previous section, we propose an information leakage definition for
realistic attack scenarios to model two types of address-based side-channel
leakages and showed how to quantify them by calculating the number of input
keys ($K^o$) that satisfy the formulas. Intuitively, we can use
symbolic execution to capture math formulas and model counting
to obtain the number of satisfying input keys ($K^o$). However, preliminary
experiments showed that this approach was far too expensive to use with real-world
applications. In this section, we discuss the bottlenecks in
this approach and propose a practical solution.

According to Definition~\ref{chapter4:def} introduced in the previous section,
the problem of quantifying the amount of leaked information can be reduced to
the problem of computing the number of items in $K^o$. However, we find that while
there are various propositional model counters (e.g., \#SAT), they are not
sufficient scalable for production cryptosystem analysis.
there is no open source modulo theories counter (\#SMT) available.

@@

\begin{theorem}
    \label{IndependentConstraint}
    Let $g_{1}, g_{2}, \ldots, g_{m}$ be a maximum independent partition of
    $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
    $K_c$ is the input set that satisfies constraint $c$. We have the following
    equation in regard to the size of $K_c$
    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}|*|K_{g_{2}}|*\ldots*|K_{g_{n}}|$$
\end{theorem}
With Theorem~\ref{IndependentConstraint}, we change the problem of
counting the number of solutions to a complicated constraint in a high-dimension
space into counting solutions to several small constraints. We compute the
maximum independent partition by iterating each $\addr{i}$ and applying the function
$\pi$ over the constraint $\addr{i}$.

@@

@@

    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * range(k))$
    \caption{Multiple Step Monte Carlo Sampling}
\end{algorithm}
\DecMargin{1em}

@@

    %    \resizebox{1.9\columnwidth}{!}{
    \begin{threeparttable}
        \begin{tabular}{l@{}r@{~~}rrr@{~~}rr}
            \hline
            \textbf{Name}     & \textbf{\# Leaks}        & \textbf{\# CF} & \textbf{\# DF}
                              & \textbf{\# Instructions} & \textbf{SE}    & \textbf{MC}                                      \\\hline
                              &                          &                &                &             & ms      & ms      \\\cline{6-7}
            AES\tnote{1}      & 68                       & 0              & 68             & 39,855      & 512     & 1,052   \\
            AES\tnote{2}      & 68                       & 0              & 68             & 39,855      & 520     & 1,057   \\
            AES\tnote{4}      & 75                       & 0              & 75             & 1,704       & 231     & 9,199   \\
            AES\tnote{5}      & 88                       & 0              & 88             & 1,350       & 36      & 1,924   \\
            AES\tnote{6}      & 88                       & 0              & 88             & 1,350       & 35      & 1,961   \\
            AES\tnote{7}      & 88                       & 0              & 88             & 1,420       & 36      & 2,161   \\
            AES\tnote{8}      & 88                       & 0              & 88             & 1,586       & 43      & 1,631   \\
            DES\tnote{1}      & 15                       & 0              & 15             & 4,596       & 58      & 162     \\
            DES\tnote{2}      & 15                       & 0              & 15             & 4,596       & 57      & 162     \\
            DES\tnote{4}      & 6                        & 0              & 6              & 2,976       & 163     & 4,677   \\
            DES\tnote{5}      & 8                        & 0              & 8              & 2,593       & 166     & 6,509   \\
            DES\tnote{6}      & 8                        & 0              & 8              & 2,593       & 165     & 5,975   \\
            DES\tnote{7}      & 8                        & 0              & 8              & 4,260       & 182     & 5,292   \\
            DES\tnote{8}      & 6                        & 0              & 6              & 8,272       & 229     & 5,152   \\
                              &                          &                &                &             & seconds & seconds \\\cline{6-7}
            Chacha20\tnote{3} & 0                        & 0              & 0              & 149,353     & 2       & 0       \\
            Poly1305\tnote{3} & 0                        & 0              & 0              & 1,213,937   & 15      & 0       \\
            Argon2i\tnote{3}  & 0                        & 0              & 0              & 4,595,142   & 37      & 0       \\
            Ed25519\tnote{3}  & 0                        & 0              & 0              & 5,713,619   & 271     & 0       \\
            ECDSA\tnote{1}    & 6                        & 6              & 0              & 4,214,946   & 48      & 31      \\
            ECDSA\tnote{2}    & 4                        & 4              & 0              & 4,192,558   & 102     & 1639    \\
            ECDSA\tnote{5}    & 5                        & 4              & 1              & 8,248,322   & 101     & 62      \\
            ECDSA\tnote{6}    & 5                        & 4              & 1              & 8,263,599   & 100     & 58      \\
            ECDSA\tnote{7}    & 5                        & 4              & 1              & 6,100,465   & 76      & 42      \\
            ECDSA\tnote{8}    & 0                        & 0              & 0              & 10,244,076  & 121     & 0       \\
            ECDSA\tnote{9}    & 0                        & 0              & 0              & 9,266,191   & 102     & 59      \\

                              &                          &                &                &             & minutes & minutes \\\cline{6-7}
            RSA\tnote{1}      & 6                        & 6              & 0              & 22,109,246  & 39      & 41      \\
            RSA\tnote{2}      & 12                       & 12             & 0              & 24,484,441  & 44      & 251     \\
            RSA\tnote{4}      & 107                      & 105            & 2              & 17,002,523  & 23      & 428     \\
            RSA\tnote{5}      & 38                       & 27             & 11             & 14,468,307  & 29      & 436     \\
            RSA\tnote{6}      & 36                       & 27             & 9              & 15,285,210  & 40      & 714     \\
            RSA\tnote{7}      & 31                       & 22             & 9              & 16,390,750  & 34      & 490     \\
            RSA\tnote{8}      & 4                        & 4              & 0              & 18,207,016  & 8       & 53      \\
            RSA\tnote{9}      & 8                        & 8              & 0              & 18,536,796  & 5       & 780     \\
            RSA\tnote{10}     & 11                       & 9              & 2              & 9,527,231   & 2       & 38      \\
            RSA\tnote{11}     & 14                       & 14             & 0              & 10,513,606  & 14      & 503     \\
            RSA\tnote{12}     & 8                        & 8              & 0              & 27,407,986  & 113     & 6560    \\
